Hidden Talents in Context: Multiverse analysis repository

### 2022-01-31 manuscript/manuscript.Rmd
CD revision 1, add citation

Hidden talents may also emerge when testing *content and stimuli* are more ecologically relevant and concrete. Typical cognitive tests use abstract content that is largely detached from the real world. Such abstract materials may disadvantage youth whose childhood experiences involve less abstract, analytical problem solving [@ellis2020; @frankenhuis2013]. Cultural psychologists and anthropologists have demonstrated this fact across the world. For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001]. This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests. In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016]. These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?

>>>>

Hidden talents may also emerge when testing *content and stimuli* are more ecologically relevant and concrete. Typical cognitive tests use abstract content that is largely detached from the real world. Such abstract materials may disadvantage youth whose childhood experiences involve less abstract, analytical problem solving [@ellis2020; @frankenhuis2013]. Cultural psychologists and anthropologists have demonstrated this fact across the world. For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001]. This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests. In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@miller-cotto2021; @doebel2020; @zuilkowski2016]. These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?
